### 2020-05-07 README.Rmd
first commit

The other datsets were obtained from the [Homeland Infrastructure Foundation](https://hifld-geoplatform.opendata.arcgis.com/datasets/hospitals/data?page=18), the [Census](https://data.census.gov/cedsci/table?q=United%20States), [Mapping Medicare Disparities](https://data.cms.gov/mapping-medicare-disparities), and [activity indexes](https://github.com/COVIDExposureIndices/COVIDExposureIndices) calculated by  Victor Couture, Jonathan Dingel, Allison Green, Jessie Handbury, and Kevin Williams based on smartphone movement data provided by `PlaceIQ`. Emissions of pm2.5 in micro g/m3 (2016) were reported by \href{http://fizz.phys.dal.ca/~atmos/martin/?page_id=140#V4.NA.02.MAPLE}{Atmoshpheric Composition Analysis Group} and
#'  aggregate by \href{https://github.com/wxwx1993/PM_COVID/blob/master/additional_preprocessing_code/download_pm25_values.md}{Ista Zahn and Ben Sabath}

@@

* `us_acm_househ`: several metric regarding household composition, including poverty, education, ancestry (2018).
* `us_age_sex`: age and sex distribution (2018).
* `us_fl65`:  percentage of fee-for-service (FFS) Medicare enrollees that had an annual flu vaccination (2017)
* `us_hospbeds`: total hospital beds in each county (2019).
* `us_netinc`: median househould income (2018).
* `us_mmd`: data of 2017 regarding the  prevalence found in medicare beneficiaries of 
    * many medical and chronic conditions (Alzheimer, chronic kidney, obesity, depression, obstructive pulmonary, disease, arthritis, diabetes, osteoporosis, asthma, atrial  fibrillation, ischemic hearth, myocardial infarction, hypertension).
    * several type of cancer.
    * emergency,  medical admissions and annual visits.
    * pneumoccocal vaccine.
    * tobacco use.
* `us_pm2.5`: Emissions of pm2.5 in micro g/m3
* `us_race`: estimated races in population (2018).

@@

Demographic metrics and other stats regarding medical conditions and vaccinations were obtained from the [ISTAT](http://dati.istat.it/?lang=en), [Ministero della Salute](http://www.salute.gov.it/portale/home.html). Data regarding `pm2.5` were collected by [Istituto Superiore Per La protexione Ambientale](https://annuario.isprambiente.it/pon/basic/14)

@@

* `it_bweight`: Body mass index in regions of Italy, in the general population.
* `it_cancer`: Number of cancer patients in each region by type.
* `it_chronic`: Number of people suffering of chronic conditions by region and type.
* `it_dem`: Number of people by region, sex, age.
* `it_firstaid`: Number of people using first aid or medical guard (3 months). 
* `it_fl`: Influenza vaccination coverage in Italy for 2009-2019 season for general population and aged 65 and more.
* `it_fl_2019`: Influenza vaccination coverage in Italy for 2018-2019 season for general population and 65 and more.
* `it_hospbed`: Inpatient hospital beds per 1000 people.
* `it_house`:  household crowding index from 2014 to 2018 in each region.
* `it_netinc`:  median net annual households income (including imputed rents, in euros).
* `it_pm2.5`:  emission of particulate 2.5 in tons per region.
* `it_regions`: Area in square meters of each region. Used to calculate density per region.
* `it_smoking`: Number of people aged 14 years and over that self-referred as smoker, non smoker, or past smoker by region.

>>>>

The other datsets were obtained from the [Homeland Infrastructure Foundation](https://hifld-geoplatform.opendata.arcgis.com/datasets/hospitals/data?page=18), the [Census](https://data.census.gov/cedsci/table?q=United%20States), [Mapping Medicare Disparities](https://data.cms.gov/mapping-medicare-disparities), and [activity indexes](https://github.com/COVIDExposureIndices/COVIDExposureIndices) calculated by  Victor Couture, Jonathan Dingel, Allison Green, Jessie Handbury, and Kevin Williams based on smartphone movement data provided by `PlaceIQ`. Emissions of pm2.5 in micro g/m3 (2016) were reported by \href{http://fizz.phys.dal.ca/~atmos/martin/?page_id=140#V4.NA.02.MAPLE}{Atmoshpheric Composition Analysis Group} and aggregate by [Ista Zahn and Ben Sabath.](https://github.com/wxwx1993/PM_COVID/blob/master/additional_preprocessing_code/download_pm25_values.md)

@@

* `us_acm_househ`: several metric regarding household composition, including poverty, education, ancestry (2018).
* `us_age_sex`: age and sex distribution (2018).
* `us_hospbeds`: total hospital beds in each county (2019).
* `us_netinc`: median househould income (2018).
* `us_mmd`: data of 2017 regarding the  prevalence found in medicare beneficiaries of 
    * many medical and chronic conditions (Alzheimer, chronic kidney, obesity, depression, obstructive pulmonary, disease, arthritis, diabetes, osteoporosis, asthma, atrial  fibrillation, ischemic hearth, myocardial infarction, hypertension).
    * several type of cancer.
    * emergency,  medical admissions and annual visits.
    * tobacco use.
* `us_pm2.5`: Emissions of pm2.5 in micro g/m3
* `us_race`: estimated races in population (2018).

@@

Demographic metrics and other stats regarding medical conditions were obtained from the [ISTAT](http://dati.istat.it/?lang=en), [Ministero della Salute](http://www.salute.gov.it/portale/home.html). Data regarding `pm2.5` were collected by [Istituto Superiore Per La protexione Ambientale](https://annuario.isprambiente.it/pon/basic/14)

@@

* `it_bweight`: Body mass index in regions of Italy, in the general population.
* `it_cancer`: Number of cancer patients in each region by type.
* `it_chronic`: Number of people suffering of chronic conditions by region and type.
* `it_dem`: Number of people by region, sex, age.
* `it_firstaid`: Number of people using first aid or medical guard (3 months). 
* `it_hospbed`: Inpatient hospital beds per 1000 people.
* `it_house`:  household crowding index from 2014 to 2018 in each region.
* `it_netinc`:  median net annual households income (including imputed rents, in euros).
* `it_pm2.5`:  emission of particulate 2.5 in tons per region.
* `it_regions`: Area in square meters of each region. Used to calculate density per region.
* `it_smoking`: Number of people aged 14 years and over that self-referred as smoker, non smoker, or past smoker by region.
